---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# djprtradedash

<!-- badges: start -->

[![R-CMD-check](https://github.com/djpr-data/djprtradedash/workflows/R-CMD-check/badge.svg)](https://github.com/djpr-data/djprtradedash/actions) [![Codecov test coverage](https://codecov.io/gh/djpr-data/djprtradedash/branch/main/graph/badge.svg)](https://app.codecov.io/gh/djpr-data/djprtradedash?branch=main)

<!-- badges: end -->

The [DJPR Trade Dashboard](https://djpr-spp.shinyapps.io/djprtradedash/) provides a convenient way for users to browse publicly-accessible data about Victorian exports and imports.

## Installing the package

Install from GitHub with:   
```{r, eval=FALSE}
if (!requireNamespace("remotes")) {
  install.packages("remotes")
}

remotes::install_github("djpr-data/djprtradedash", dependencies = TRUE)
```

  

```{r}
library(djprtradedash)
```

## Data functions

`djprtradedash` contains functions to download and tidy trade data from publicly-available sources such as the ABS.

Import ABS balance of payments data by State/Territory with `read_bop()`:

```{r}
read_bop()
```

Import ABS merchandise exports data with `read_merch()`:

```{r}
read_merch(min_date = as.Date("2021-01-01"),
                          max_date = as.Date("2021-02-01"))
```

Import ABS International Trade Supplementary Information with `read_supp()`:

```{r}
read_supp("cy", 3)
```

## Data objects

The file `data-raw/create_dash_data.R` uses the data functions (see above) to download and tidy data. That data is then stored as internal data objects in this package.

-   `merch` is merchandise exports data from `read_merch()`

-   `bop` is balance of payments data from `read_bop()`

-   `supp_cy` is supplementary calendar year trade information from `read_supp("cy")`

-   `supp_fy` is supplementary financial year trade information from `read_supp("fy")`
